What do incoming university students believe about open science practices in

### 2021-04-16 analysis/Manuscript.Rmd
add the correlations and CI to the norm & counternorm table

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@

@@

```{r, difference between norm and counternorm}

@@

# combine means & SDs
prac_means$Practice <- prac_means$practice
prac_means$Norm <- paste0(round_tidy(prac_means$norm_mean,2),
                          " (", 
                          round_tidy(prac_means$norm_sd,2), 
                          ")")
prac_means$Counternorm <- paste0(round_tidy(prac_means$cnorm_mean,2), 
                            " (", 
                            round_tidy(prac_means$cnorm_sd,2), 
                            ")")
prac_means$Difference <- paste0(round_tidy(prac_means$diff_mean,2), 
                            " (", 
                            round_tidy(prac_means$diff_sd,2),
                            ")", 
                            " [",
                            round_tidy(prac_means$lower,2),
                            ", ", 
                            round_tidy(prac_means$upper,2),
                            "]")

# clean it up into a new dataframe with only the columns we need
practice_means <- prac_means %>% 
  dplyr::select(Practice, Norm, Counternorm, Difference)

@@

# notes for the correlations....
# just the correlation with CI
critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)

#correlation test with CI and p-values in a clean tibble
critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
# tidy(critical_corr_test)

@@

# this will create a tibble for each practice and then calculate

@@

# breadcrumbs: keep the values that I need from this tibble
# use p_tidy? to clean up the pvalues
# round the corr & CI
# join with the practice_means tibble & turn into a table

@@

knitr::kable(practice_means,
             caption = "Means (sd) for norms, counternorms, and the difference between the two for each of the practices",
             digits = 2,
             align = c('lccc'))

@@

>>>>

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@

```{r functions}

p_tidy <- function (x, digits, prefix = "= ") {
    x.out = paste0(prefix, round_tidy(x, digits))
    all_zeros = paste0(prefix, round_tidy(0, digits))
    less_than = paste0("< ", format(10^-digits, scientific = FALSE))
    x.out[x.out == all_zeros] = less_than
    return(x.out)
}
```

@@

```{r difference between norm and counternorm}

@@

# combine means & SDs
prac_means$Norm <- paste0(round_tidy(prac_means$norm_mean,2),
                          " (", 
                          round_tidy(prac_means$norm_sd,2), 
                          ")")
prac_means$Counternorm <- paste0(round_tidy(prac_means$cnorm_mean,2), 
                            " (", 
                            round_tidy(prac_means$cnorm_sd,2), 
                            ")")
prac_means$Difference <- paste0(round_tidy(prac_means$diff_mean,2), 
                            " (", 
                            round_tidy(prac_means$diff_sd,2),
                            ")", 
                            " [",
                            round_tidy(prac_means$lower,2),
                            ", ", 
                            round_tidy(prac_means$upper,2),
                            "]")

# clean it up into a new dataframe with only the columns we need
practice_means <- prac_means %>% 
  dplyr::select(practice, Norm, Counternorm, Difference)

@@

# notes for the correlations....
# just the correlation with CI
# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)

#correlation test with CI and p-values in a clean tibble
# critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
# tidy(critical_corr_test)

@@

# this will create a tibble for each practice

@@

# remove unnecessary columns, round the values, and move columns
corr <- corr %>% 
  dplyr::select(-c(data, test, statistic, parameter, method, alternative))  %>% 
  mutate(p.value = p_tidy(p.value, 3, prefix = "")) %>% 
  mutate(estimate = round_tidy(estimate,2), 
         conf.low = round_tidy(conf.low, 2), 
         conf.high = round_tidy(conf.high, 2)) %>% 
  dplyr::relocate(estimate, .before = conf.low) %>%  
    dplyr::relocate(p.value, .after = last_col())

# join the corr tibble with the means tibble 
practice_means_corr <- practice_means %>% inner_join(corr, by = "practice")

# combine the confidence intervals into one column
practice_means_corr$Correlation <- paste0(practice_means_corr$estimate, 
                            " [",
                            practice_means_corr$conf.low,
                            ", ", 
                            practice_means_corr$conf.high,
                            "]")

# clean up the tibble                          
practice_means_corr <- practice_means_corr %>% 
  mutate(Practice = practice) %>% 
  dplyr::select(-c(practice,estimate, conf.low, conf.high)) %>% 
  relocate (Practice, .before = Norm) %>% 
  relocate (p.value, .after = last_col())

# breadcrumbs: keep the values that I need from this tibble
# use p_tidy? to clean up the pvalues {done!}
# round the corr & CI {done!}
# join with the practice_means tibble & turn into a table {done!}
# need to figure out whether I can rotate a page in papaja

@@

knitr::kable(practice_means_corr,
             caption = "Means (sd) for norms, counternorms, the difference between norms and counternorms, and correlations between norms and counternorms",
             digits = 2,
             align = c('lccc'))

@@

<!-- I imagine we will remove the p.value column, but we might want this for now.  -->
